Neuroanatomical priors improve image-based cortical thickness computation: ROI-DiReCT

### 2015-10-29 manuscript.tex
Discussion
Discussion

For a single label,
\begin{align}
  E(\phi(\mathbf{x},1)) = \int_0^1 \|\mathbf{v}(\mathbf{x},t)\|^2 dt +
      \|P_w(\mathbf{x}) -P_{wg}(\mathbf{x})\|^2
\end{align}

\begin{align}
  \sum_{n=1}^N E_{n}(\phi_n(\mathbf{x},1))
\end{align}

\section*{Discussion} 
%This should explore the significance of the results of the work, not repeat them. A combined Results and Discussion section is often appropriate. Avoid extensive citations and discussion of published literature.

>>>>

\section*{Discussion}

\subsection*{Working memory networks}

Working memory is the result of various combinations of processes, no processes ((and correspondingly no brain structures)are unique or speciﬁc to working memory. ( Eriksson, 2015)Many brain regions interact during working memory andinclude "executive" regions in the PFC, parietal cortex, and basal ganglia, as well as regions specialized for processing the particular representations to be maintained, such as the fusiform face area for maintaining face information. Persistent neural activity in various brain regions accompanies working memory and is functionally necessary for maintenance and integration of information in working memory.

The organization of human WM has long been the topic of psychological models (Atkinson and Shiffrin, 1968; Hebb, 1949), with maybe the most inﬂuential having been proposed by Baddeley and Hitch (1974). In Rottschy,2012, the WM network was identified by functional neuroimaging using quantiattive coordiante-based meta-analysis over almost 200 individual experiments. By pooling various working memory tasks, a main network was identified which mainly comprise the fronto-parietal network. By eliminating the effect of specific task designs and contrasts, a more restricted "core" network emerged from conjunctions analyses. A core network independently of the specific aspects and task features was identified using conjunction analysis. This network mainly comprise the dorsal area 44, anterior insula, (pre-)SMA and IPS. The dorsal areas 44/45 and the pre-SMA are part of the phonological loop, a subsystem that response for verbal working memory material maintenance. There has been evidence that the dorsal region of Broca's area is active only during the first part of the delay period, and is involved in the formation of an articulatory rehearsal program. Generally, the same brain regions dedicated to sensory processing are believed to store sensory information during delay periods and working-memory task performance. A conjunction of verbal vs. non-verbal material in Rottschy's study revealed that the BA44/45 area may also involed in non-verbal WM tasks, that it may not be a modality-specific area in working memory. The reduced functional connectivity may underpin the verbal working memory deficits in schizophrenia. The previous research has established that the PFC is causally involved in normal working  memory functioning. However, there is yet no consensus on the details of the functional organization of the PFC. The absent of DLPFC, which is believed to an neuro agent for the central executve module in Baddeley and Hitch's model in Rottschy's core network, may be due to some working memory task requires little manipulation process of the memory content. In fact, the lateral PFC clusters in the main network was subdivided to two, that the abstraction level of goals and task rules are suggested to peak in rostral PFC and decrease to the caudal part. The caudal LPFC register a working memory load effect while the rostral part was not.
